openarchaeoCollaboration

### 2023-01-30 analysis/paper.qmd
Add missing dependency

```{r dependencies, include=FALSE}
library("tidyverse")
library("lubridate")
library("openarchaeoCollaboration")
library("khroma")
library("gt")
library("fs")
library("here")
library("tidygraph")
library("ggraph")
```

>>>>

```{r dependencies, include=FALSE}
library("tidyverse")
library("lubridate")
library("openarchaeoCollaboration")
library("khroma")
library("gt")
library("fs")
library("here")
library("tidygraph")
library("ggraph")
library("ggiraph")
```
